Hurricane Evacuation Strategies for the State of Mississippi

### 2015-11-16 manuscript.tex
nothing to see here

\section{Introduction}
\label{sec:introduction}
  The Mississippi Emergency Management Administration (MSEMA) has hired our team to design hurricane evacuation routes for at-risk counties in the coastal regions of southern Mississippi. Given that this coastal area is a strong commercial center, the government authorities want us to minimize the number of unnecessary evacuations. Under this requirement, it is more advantageous to withhold ordering an evacuation for as long as safely possible. The reasons for this are two-fold. First, this ensures that local businesses can remain open for as long as possible. Second, this ensures that the forecasts at the time of the evacuation decision are as accurate as possible. Therefore, our models seek to recommend an optimal evacuation plan as well as the latest possible time at which it is safe to enact this plan.

@@

\section{Future Work}
\label{sec:future}
The first aspect that we would like to focus on in the future had we had more time would be the interactions between Mississippi and its surrounding states. It is probable that in the event of a state wide evacuation, the transportation system would need to support not just the citizens of Mississippi but also those of Louisiana and Alabama.
\newline
In addition to this, we would like to do more robustness testing by generating random hurricanes and their trajectories, and plan accordingly. This would allow us to test on a much bigger data sample than the one we were able to get our hands on.
\newline
Another area that we would have liked to improve has to do with the fact that we did not take into account the trajectory of the hurricanes after they made landfall. We considered that by that time, the populations of the counties affected should have been evacuated according to the level of emergency that we assigned them.\newline
Overall, all of these would be achievable with the state of our models, but would require a lot of time to polish as it would add a significant amount of complexity to the simulations.

>>>>

\section{Introduction}
\label{sec:introduction}
  The Mississippi Emergency Management Administration (MSEMA) has hired our team to design hurricane evacuation routes for at-risk counties in the coastal regions of southern Mississippi. Given that this coastal area is a strong commercial center, the government authorities want us to minimize the number of unnecessary evacuations. Under this requirement, it is more advantageous to withhold ordering an evacuation for as long as is safely possible. The reasons for this are two-fold. First, this ensures that local businesses can remain open for as long as possible. Second, this ensures that the forecasts at the time of the evacuation decision are as accurate as possible. Therefore, our models seek to recommend an optimal evacuation plan as well as the latest possible time at which it is safe to enact this plan.

@@

\section{Future Work}
\label{sec:future}
